Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-18 minimax.tex
solved warning
Further reduction and small modifs

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}
\usepackage{times}
\usepackage{soul}
\usepackage{amsthm}
\usepackage[hidelinks]{hyperref}

@@

\section{Interactive Elicitation} 
\label{sec:elicit}
We propose an incremental elicitation method based on minimax regret.
At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or until it drops to zero if we wish optimality).

@@

\paragraph{Building concrete questions for the chair}
Even if the chair might be considered able to answer such abstract questions, we consider important to make sure that these questions can also be asked in a more concrete way: in terms of winners of example profiles. Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights. A large stream of research considers more meaningful to ask direct choice questions ("please choose either a or b") than to question the decision maker about the shape of its utility function. The former are considered "observable": acts of choice are translated to preference statements. In the social choice context, this way of asking questions has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process is novel. Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Asking questions about weights only works when a scoring rule is being considered.

Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
\begin{proposition}\label{prop:chairQuestions}
	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
\end{proposition}
See the proof of construction in \cref{proof:chairQuestions}.

\begin{example*}
	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
	We then show the following profile to the chair and ask who should win (each column is a preference of a voter).
	\begin{center}
		$
		\begin{array}{ccccccccc}
			c&d&d&a&a&a&b&b&b\\
			a&c&c&b&b&b&a&a&a\\
			b&b&b&c&c&c&d&d&d\\
			d&a&a&d&d&d&c&c&c\\
		\end{array}.
		$
	\end{center}
	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
\end{example*}

\paragraph{Elicitation strategies}
We develop several elicitation strategies for simultaneous elicitation of agent preferences and of the scoring rule.
While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate experimentally approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question should be asked next.

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
This strategy first chooses equiprobably whether it will ask a question about weights or a question about a preference ordering. If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative. 
The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
The candidate questions to the agents are chosen following the idea of \citet{Lu2011}: in order to increase $\PMR(x^{*},\bar{y})$, the adversary should place as many alternatives as possible above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.
For each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random. 
%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$. We provide more details in \cref{sec:appendix}.

@@

Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m - 1$ questions to each agent in turn. 
Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that is currently incomparable to this alternative. This approach guarantees that the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
This strategy can be expected to perform well when the chair assigns a large weight to the first rank, as compared to the other ranks. It will be useful to further challenge the Pessimistic strategy, which is not specifically tailored to such a situation.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
%We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
We used both real data-sets and generated profiles. In the latter case, we pick a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we then randomly generate an “oracle”, representing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. IC is a quite challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles. The real preferences are downloaded from \textit{PrefLib: A Library for Preferences} \citep{PrefLib} and passed to the oracle. In particular, we used the following data-sets: \textit{T Shirt} (11 T-Shirt designs (m) voted by 30 members (n) of the Optimization Research Group at NICTA), \textit{AGH Course Selection} (9 courses (m) evaluated by 146 students (n) of the AGH University) and Skate (14 skaters (m) evaluated by 9 judges (n) at the Euros Pairs Short Program).
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For both real and generated data-sets we generate the weights of the scoring rule. We first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents and the weight differences favored by the chair. We obtain the first question to be asked using the strategy under test. We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question. This is repeated until $k$ answers have been obtained, computing the resulting MMR values along the way for various values of $k$. We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}. The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.

@@

\begin{details*}[Pessimistic]
	Once having selected $n + m$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative. 
	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
	We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions. We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
	To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
	Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
	%The motivation for using this operator lies in 
	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
	(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)
\end{details*}

>>>>

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}
\usepackage{times}
\usepackage{soul}
\usepackage[hidelinks,hypertexnames=false]{hyperref}
\usepackage{amsthm}

@@

\section{Interactive Elicitation} 
\label{sec:elicit}
We propose an incremental elicitation method based on minimax regret.
At each step, the system may ask a question either to one of the agents about her preferences or to the chair about the voting rule. 
The goal is to obtain relevant information to reduce minimax regret as quickly as possible.
The elicitation can be terminated either after a given number of questions, or when the minimax regret is lower than a threshold (or when it drops to zero if we wish optimality).

@@

\paragraph{Building concrete questions for the chair}
Even if the chair might be considered able to answer directly such abstract questions, we want to ensure that these questions can also, in principle, be asked in a more concrete way: in terms of winners of example profiles. Such questions have precise semantics whose understanding can be assumed to be shared by the chair, contrary to abstract questions about weights. 
Moreover, this way of questioning the chair is independent of the voting rule that is being elicited. Asking questions about weights only works when a scoring rule is being considered.
Asking who should win in specific profiles has been used in experimental settings investigating the feeling of justice of individuals \citep{Giritligil2005}, but, to the best of our knowledge, the use of such questions to systematically guide an elicitation process about voting rules is novel. 
This is similar to favor, in decision theory, direct choice questions ("please choose either a or b") compared to questioning the decision maker about the shape of her utility function. The former are considered “observable”: acts of choice are translated to preference statements \citep{colell_microeconomic_1995}.

Thus, our task is to build a profile, given $\lambda$ and $r ≤ m-2$, in such a way that the set of (tied) winners picked by the chair reveals whether $w_{r} - w_{r+1} \geq \lambda (w_{r+1} - w_{r+2})$.
\begin{proposition}\label{prop:chairQuestions}
	Given a rational $\lambda = p/q > 1$ and a rank $r$ between $1$ and $m - 2$, there exists a profile $P$ such that, for any weight vector $\w \in \W$, $a \in f(P)$ iff $w_{r} - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$ and $b \in f(P)$ iff $w_{r} - w_{r+1} ≤ \lambda (w_{r+1} - w_{r+2})$, where $f$ is the PSR parameterized with $\w$.
\end{proposition}

\begin{example*}
	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. 
	We then show the following profile to the chair and ask who should win (each column is a preference of a voter).
	\begin{center}
		$
		\begin{array}{ccccccccc}
			c&d&d&a&a&a&b&b&b\\
			a&c&c&b&b&b&a&a&a\\
			b&b&b&c&c&c&d&d&d\\
			d&a&a&d&d&d&c&c&c\\
		\end{array}.
		$
	\end{center}
	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
	(\cref{proof:chairQuestions} presents the general method of constructing such profile.)
\end{example*}

\paragraph{Elicitation strategies}
We develop several strategies for simultaneous elicitation of agent preferences and of the PSR.
While it is of course possible to first fully elicit the agent preferences and afterwards elicit weights, we want to investigate experimentally approaches that are able to recommend winning alternatives before obtaining complete knowledge of the profile or the rule.
%Indeed, it can be beneficial to split efforts asking questions to the chair and to agents, depending on which is estimated to be more informative.
We define here the various strategies we tested experimentally. A strategy tells us, given the current partial knowledge $(\pprofile, W)$, which question to ask next.

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
It first chooses equiprobably whether to question the chair or the agents. In the first case, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$.
%The intervals are initialized to $[1, n]$: $\lambda≥1$ by convexity and we assume $\lambda≤n$ wlog, in fact for $\lambda≥n$, the rule coincides with Plurality.
In the second case, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices. 
The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank \commentOC{Isn’t this $m-2$?}.
The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$. \Cref{sec:appendix} provides more details.

@@

Finally, the \strat{Elitist} strategy aims at uncovering as quickly as possible the top alternative of each agent. It asks $m - 1$ questions to each agent in turn. 
Given an agent to query $j$, it asks about an alternative currently undominated in $\ppref_j$ and any alternative that is currently incomparable to this alternative. Thus, the top alternative in the ranking of $j$ will be known after having asked exactly $m-1$ questions to $j$.
After having asked $n (m-1)$ questions to the agents, it questions the chair only, using the same approach as the Pessimistic strategy.
This strategy can be expected to perform well when the chair assigns a large weight to the first rank, as compared to the other ranks. It will be useful to further challenge the Pessimistic strategy, which is not specifically tailored to such a situation.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
We  performed a number of numerical experiments using both real data and generated profiles in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
%We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.

Given a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we first create an “oracle”, representing the true preferences of the agents (randomly generated or coming from real data) and the weights associated with the chair’s scoring rule (randomly generated).
We start with empty knowledge ($\pprofile = (\emptyset, \emptyset, …), W = \W$) about the preference orderings of the agents and the weight differences favored by the chair. We obtain the first question to be asked using the strategy under test. We then use the oracle to answer the question and update the system's knowledge, which is thus used to obtain the next question. This is repeated until $k$ answers have been obtained, computing the resulting MMR values along the way for various values of $k$. We repeat this whole experiment a variable number of times indicated below, for a given $(m, n, k)$, and report the average resulting MMR and the standard deviation \textit{sd}. The sizes of the considered scenarios are comparable to the ones used by \citet{Cailloux2014}.

The oracle is built as follows. 
For the real preferences, we used the following data sets from \href{https://www.preflib.org/}{PrefLib} \citep{PrefLib}. \textit{T Shirt}: $m = 11$ tee shirt designs voted by $n = 30$ members of the Optimization Research Group at NICTA \commentOC{refs for these data sets?}; \textit{AGH Course Selection}: $m = 9$ courses evaluated by $n = 146$ students of the AGH University; and \emph{Skate}: $m = 14$ skaters evaluated by $n = 9$ judges at the Euros Pairs Short Program.
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For the generated preferences, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn independently and all have the same probability of appearing. We adopt IC because it is a more challenging situation: as can be expected intuitively (and shown in \cref{fig:linearity}), the number of questions to be asked decrease with less varied profiles. 
To generate the weights of the scoring rule, we first draw $m - 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weight is then obtained by a decumulative sum.

@@

\begin{details*}[Pessimistic]
	Given $j \in N^*$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random. 
%Responses to questions involving $x^*$ or $\bar{y}$ constrain the ability of the adversary to complete the profile in such manner, possibly reducing minimax regret.
	Once having selected $n + m$ candidate questions, the Pessimistic strategy selects the one that leads to minimal regret in the worst case, considering both possible answers to the question, and with penalty terms depending on the kind of question. To define this comparison precisely, assume that a question $q_1$ has type $t_1$ (being “chair” or “agent”), and leads to the new knowledge states $(\pprofile_1, W_1)$ if answered positively and $(\pprofile'_1, W'_1)$ if the answer is negative. 
	Define $R^{\max}_1 = \max\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)}$
	and $R^{\min}_1 = \min\set{\MMR(\pprofile_1, W_1), \MMR(\pprofile'_1, W'_1)} \epsilon_{t} + \epsilon'_{t}$.
	%If $(\pprofile_1, W_1) ≥ (\pprofile'_1, W'_1)$, define $\MMR^{\max} = \MMR(\pprofile_1, W_1)$ and $\MMR^{\min} = \MMR(\pprofile'_1, W'_1)$; otherwise, define $\MMR^{\max} = \MMR(\pprofile'_1, W'_1)$ and $\MMR^{\min} = \MMR(\pprofile_1, W_1)$.
	% and and $(\pprofile^\min_2, W^\min_2)$. numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
	The terms $\epsilon_t$ and $\epsilon'_{t}$ are real numbers associated to the type $t$ of question; these parameters are to be determined experimentally and are used to fine control the choice of the question type.
	Define similarly $t_2$, $R^{\max}_2$ and $R^{\min}_2$ for a question $q_2$.
	We are now faced with the problem of aggregating these values in order to compare the informative values of the candidate questions. We adopt a pessimistic approach, reported to perform better than optimistic aggregation \citep{Cailloux2014}, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
	To avoid the absorption property of the max, we adopt $\leximax$ as an aggregator.
	Pessimistic thus considers question $q_1$ to be better  than $q_2$ iff $R^{\max}_1 < R^{\max}_2 \text{ or } [R^{\max}_1 = R^{\max}_2 \text{ and } R^{\min}_1 < R^{\min}_2]$.
	%This comparison gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
	%The motivation for using this operator lies in 
	In other words if the maximal {\em a posteriori} MMR of two questions are (nearly) equal, then it considers the (penalized) minimal MMR values, preferring the question with the lowest value.
	(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the penalized minimal MMR values, with a predominant weight given to the maximal one, several order of magnitudes higher than the weight given to the penalized minimal MMR.)

The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
\end{details*}
